A survey of HTTP caching options on the open Web

### 2014-12-17 sanity/paper1.tex
smaller changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@905 43ef1190-90fd-4dd7-a769-d0121f02b80e
spellcheck
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@906 43ef1190-90fd-4dd7-a769-d0121f02b80e

\documentclass{llncs}
%\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage{wrapfig}

@@

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}

\subtitle{---Unpublished Working Draft, do not circulate---}

@@

LDF\todo{ref paper1} claims to take advantage of caching and contrasts
this with the inavailabilty of SPARQL query caches, and claims this is
an architectural problem.

@@

Then, we retrieved the dataset of the Billion Triple Challenge
2014\todo{ref}, a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. Due to the presence of invalid RDF, we
iterated through the NQuad files on a line-by-line basis. First, we
matched each line against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework \text{RDF::Trine}\todo{footnote} was used to parse
the line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \rdfterm{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \rdfterm{void:vocabulary},
\rdfterm{rdfa:vocabulary} or \rdfterm{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \rdfterm{cogs:Endpoint},
\rdfterm{owl:Ontology} and \rdfterm{voaf:Vocabulary} \todo{footnotes for
  all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

@@

We then developed a fairly elaborate paralell spider to get the
resources found on 3117 unique hosts in the previous steps using the
Perl frameworks RDF::Trine and libwww. The spider operated with a
timeout of 20 seconds and a maximum message size it would accept of 1
MB.

The paralell spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URIs. Since the BTC2014 recorded
the \httph{Expires} (an RFC7234 caching header), \httph{Last-Modified}
and \httph{ETag} (RFC7232 conditional request) headers where they
existed, we first examined if any of the resources were still fresh,
but none were. Whereever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

@@

Based on the resulting headers, we first let libwww calculate the
freshness lifetime in seconds if it was possible, and recorded
that. Then, we also let it calculate a \emph{heuristic} freshness
time based on a suggestion in RFC7234, section~4.2.2, and record that.

@@

For endpoints, we examine the response message, to see if there are
any results to our query, and record that if there are.

>>>>

%\documentclass{llncs}
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{cite}
\usepackage{verbatim}
\usepackage{graphicx}
%\usepackage{wrapfig}

@@

\title{A survey of HTTP caching options on the open Web}
\author{Kjetil Kjernsmo}%\inst{1}}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%N-0316 Oslo, Norway \email{kjetil@kjernsmo.net}

%\subtitle{---Unpublished Working Draft, do not circulate---}

@@

LDF\todo{ref paper1} claims to take advantage of caching and contrasts
this with the unavailability of SPARQL query caches, and claims this is
an architectural problem.

@@

Then, we retrieved the dataset of the Billion Triple Challenge
2014\todo{ref}, a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. Due to the presence of invalid RDF, we
iterated through the NQuad files on a line-by-line basis. First, we
matched each line against a regular expression were lines matching
\texttt{ontology|endpoint|sparql|vocabular} passed the filter. Then,
the Perl framework RDF::Trine\todo{footnote} was used to parse
the line. Lines that failed to parse was discarded. We have not
investigated whether this could introduce biases. Statements were then
accepted into a new NQuad file if they had a predicate that matched
the \rdfterm{sd:endpoint}\todo{footnote} or matched a case-insensitive
regular expression \texttt{sparql} if the subject and objects were
both resources, or the predicates \rdfterm{void:vocabulary},
\rdfterm{rdfa:vocabulary} or \rdfterm{api:vocabulary} \todo{footnotes
  for all}, as well as having an resource as object. Finally,
statements with the the classes \rdfterm{cogs:Endpoint},
\rdfterm{owl:Ontology} and \rdfterm{voaf:Vocabulary} \todo{footnotes for
  all} in the object position were also accepted. More classes and
properties were considered, but not used in the data reduction if they
did not occur in the original data.

@@

We then developed a fairly elaborate parallel spider to get the
resources found on 3117 unique hosts in the previous steps using the
Perl frameworks RDF::Trine and libwww. The spider operated with a
timeout of 20 seconds and a maximum message size it would accept of 1
MB.

The parallel spider would then launch a process per host, but each
request to one host would be delayed by 10 seconds. For each host, the
spider would go through the list of URLs found by previous steps for
that host. Since the BTC2014 recorded
the \httph{Expires} (an RFC7234 caching header), \httph{Last-Modified}
and \httph{ETag} (RFC7232 conditional request) headers where they
existed, we first examined if any of the resources were still fresh,
but none were. Wherever the last two headers existed, we added the
corresponding \httph{If-Modified-Since} and \httph{If-None-Match}
headers for a conditional initial request.

\begin{table}
\caption{Recorded HTTP headers}
 \begin{tabular}{ | l |  p{3cm} | p{5cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge Architecture Specification\todo{ref} & Draft
to allow more fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\todo{ref}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww\todo{ref}  & Header inserted by User
Agent to give details about problems with the download \\ \hline

    \hline
    \end{tabular}
\end{table}

@@

Based on the resulting headers, we first let libwww calculate the
freshness lifetime in seconds if it was possible, and recorded
that. Then, we also let it calculate a \emph{heuristic} freshness
time based on a suggestion in RFC7234, section~4.2.2, and recorded that.

@@

For endpoints, we examined the response message, to see if there are
any results to our query, and recorded that if there are.
